---
title: "webAPI"
author: "Zaida Liendeborg and Emma Wallentinsson"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{webAPI package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

The \code{webAPI} package can be used to access the Google geocode API to download coordinates and plot it on a map. The package consists of three functions that are necessary to plot the coordinates harvested from Google Geocode API into a map of different types.

## The getURL2R function

The **getURL2R** takes the postal number, names of the street, city or country in the world encoded into a url. The url then returns a json formatted geodata and then converted to an R object. Example of **getURL2R()** application:

```{r}
library(webAPI)

url1<- getURL2R("Stockholm, Sweden") #encodes the given path into a url and return a list of geodata.

attributes(url1)
```


## The get_coor function

The **get_coor** function extracts the coordinates from the R list of geodata returned from the **getURL2R** function. Below is an example of how **get_coor()** is used:

```{r}
#using the url1 object returned from getURL2R, we extract coordinates and name of place.

coor<- get_coor(url1)
coor
```

## The plot_map function

The function **plot_map** plots the coordinates returned from the **get_coor**. Users can customize their map into selectable types by specifying it to argument **typemap**. Different map types can be "terrain", "terrain-background", "satellite", "roadmap", and "hybrid". With the argument **zoom**, user can choose how they want to zoom the map.
 

```{r, fig.show='hold'}
plot_map(coor, zoom=13, typemap="roadmap")
```

